Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-03 thesis/thesis.tex
thesis: Add new corrections

\begin{equation}
  K(a, b) = \frac{1}{2 \pi h^{2}} \exp{ \left[ -\frac{1}{2}\frac{\left( a - a_{i} \right)^{2} + \left( b - b_{i} \right)^{2}}{ h^{2}} \right]}
\end{equation}

@@

PostgreSQL knows that all stars we want are located inside \verb|gaiadr2.region_302| so it does not need to query any other table.
This allows us to download data for as many regions as we want without loosing efficiency when accessing for that data.

@@

We have seen in the previous chapter that the DEC model is capable of refining the clustering selection made by K-Means.
This allows us to obtain a more precise characterization of the cluster.
Now, in order to validate our model and be able to estimate how good or bad it is,
we need a different method to characterize the studied clusters and compare our results with the validation method.

>>>>

\begin{equation}
  K(a, b) = \frac{1}{2 \pi h^{2}} \exp{ \left[ - \frac{1}{2}\frac{\left( a - a_{i} \right)^{2} + \left( b - b_{i} \right)^{2}}{ h^{2}} \right]}
\end{equation}

@@

PostgreSQL knows that all stars we want are located inside \verb|gaiadr2.region_302| so it does not need to query any other table.
This allows us to download data for as many regions as we want without loosing efficiency when accessing for that data.
% TODO: Revisar corrección de Imanol

@@

We have seen in the previous chapter that the DEC model is capable of refining the clustering selection made by K-Means
hence helping us have a more precise characterization of the cluster.
Now, in order to validate our model and be able to estimate how good or bad it is,
we need a different method to characterize the studied clusters and compare our results with the validation method.
